Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-07-13 paper/submitted/round2_png/reviewer_response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 2}

The main results in the paper are Proposition 1 and Eq. (14). These results are very close to existing results as presented in [7]. It is not clearly explained in the introduction, and in Section 2, in what sense the current results follow from [7] and in what sense they are new.

\answer{We elaborated upon the similarities with, and differences from, [7] (now [8]) in the last two paragraphs of Section 2.1.}

@@

The main theoretical section, Section 2, is vague, lacks proper structure and needs clarification. It is not clear how the high-fidelity and low-fidelity models are defined. These models should be the starting point of the section, not introduced in some proposition. Some degree of compatibility is assumed, but not explained. The proof of Proposition 1 refers to Proposition 3 in [7] which is worth stating in full in order to understand how it is employed. Given that (5) was stated as a Proposition 1, it is also natural to state the result in (14) as a proposition too.

\answer{We have made major revisions to Section 2. We moved the description of the low- and high-fidelity models earlier, to Section 2.1, and elaborated upon them. We expanded our explanation of compatibility at the end of Section 3.1. References to Propositions and proofs in [7] (now [8]) have been replicated within the manuscript and adapted to our setting. We added an additional proposition as suggested.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 3}

I'd like to actually see the statement and proof of Proposition 3 from reference 7 included in
the manuscript. It is at the crux of the proof and it's frustrating to have to go dig up that
detail.

\answer{References to Propositions and proofs in [7] (now [8]) have been replicated within the manuscript and adapted to our setting.}

### 2017-07-13 paper/submitted/round2_png/cleaned_for_submit/numerical_experiments_v5_cmame.tex
stashing files that ended up being submitted; tweaked reviewer response to take into account shifted reference number

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with first-order Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable; all variables are represented by the same basis. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.

@@

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. %Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{subfig:obsSetup} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are shown in \Cref{subfig:obsLF,subfig:obsMF1,subfig:obsMFlast}. The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_qoi/yarp.pdf}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp0.pdf}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp1.pdf}
  \label{subfig:obsMF1}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_qoi/yarp2.pdf}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_data/yarp.pdf}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \includegraphics[width=0.162\textwidth]{vs_data/yarp0.pdf}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
  \includegraphics[width=0.171\textwidth]{vs_data/yarp1.pdf}
  \label{subfig:obsMF1_2}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_data/yarp2.pdf}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
%\subfloat[MF$_1$ ($10\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF1}
%} \\
%\subfloat[MF$_3$ ($30\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF3}
%} \\
%\subfloat[MF$_6$ ($60\%$ HF)]{
%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
%  \label{subfig:svfparamMF6}
%} \\
%\subfloat[HF]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
%	\label{subfig:svfparamHF}
%}
%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare 
%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
the bottom two figures of \Cref{fig:svfRefParams}). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see 
%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

%compare MF01 and MF03, MF06 and HF
%1 and 3 look very different but have very similar true errors - different params can give similar qoi, though in this case the qoi is not close to HF; more HF doesn't necessarily decrease error, interplay between having freedom to match data and all LF regions being flat...
%6 and HF look very similar; most of HF is very flat

@@

We notice that, compared to the results in \Cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors. This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints as well as the third-order term that is ignored in the error estimate; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$. Compared to the pair of models in \Cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \Cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \Cref{eq:cdvcdrHF} and \Cref{eq:cdvcdrHF3D} is a quadratic reaction term. % KW: don't know what last part of this sentence means. what hi-fi models?
%The possibility of large inaccuracies in the error estimates of low-fidelity and mostly unrefined mixed-fidelity models suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the estimated high-fidelity QoI ($I(q_{MF},u_{MF})+\epsilon_i$) for two consecutive iterations agree to within some tolerance. % KW: what behavior? this last sentence doesn't follow from the previous one. and what predicted hi-fi QOI? Do you mean mixed-fi? I'm not sure this is a good idea. I'd probably delete this last sentence.
% or just let the reader decide how to deal with possibly inaccurate initial error estimates?

>>>>

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with first-order Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable; all variables are represented by the same basis. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.

@@

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. 
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{subfig:obsSetup} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are shown in \Cref{subfig:obsLF,subfig:obsMF1,subfig:obsMFlast}. The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}. Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.pdf}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/vs_qoi_err0_nobar.pdf}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
  \includegraphics[width=0.166\textwidth]{vs_qoi/vs_qoi_err1_nobar.pdf}
  \label{subfig:obsMF1}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_qoi/vs_qoi_err2_barnorm.pdf}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  %\includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \includegraphics[width=0.19\textwidth]{vs_data/vs_data_setup_sidetrim.pdf}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \includegraphics[width=0.162\textwidth]{vs_data/vs_data_err0_nobar.pdf}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
  \includegraphics[width=0.171\textwidth]{vs_data/vs_data_err1_nobar.pdf}
  \label{subfig:obsMF1_2}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \includegraphics[width=0.224\textwidth]{vs_data/vs_data_err2_barnorm.pdf}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
%\subfloat[MF$_1$ ($10\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF1}
%} \\
%\subfloat[MF$_3$ ($30\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF3}
%} \\
%\subfloat[MF$_6$ ($60\%$ HF)]{
%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
%  \label{subfig:svfparamMF6}
%} \\
%\subfloat[HF]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
%	\label{subfig:svfparamHF}
%}
%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare the bottom two figures of \Cref{fig:svfRefParams}). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

@@

We notice that, compared to the results in \Cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors. This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints as well as the third-order term that is ignored in the error estimate; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$. Compared to the pair of models in \Cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \Cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \Cref{eq:cdvcdrHF} and \Cref{eq:cdvcdrHF3D} is a quadratic reaction term.
